Glyph-maps for Visualizing Climate Data and Models

### 2011-09-28 paper.tex
Fix authors bug even though I don't think I should be first author

\title{Glyph-maps for Visualizing Climate Data and Models}
\author{Hadley Wickham$^1$, Heike Hofmann$^2$, Charlotte Wickham$^2$, Dianne Cook$^2$\\
$^1$ Department of Statistics, Rice University}
$^2$Department of Statistics, Iowa State University\\
$^3$ Department of Statistics, Oregon State University\\
\date{}

>>>>

\title{Glyph-maps for Visualizing Climate Data and Models}
\author{Hadley Wickham$^1$, Heike Hofmann$^2$, Charlotte Wickham$^2$, Dianne Cook$^2$\\
$^1$Department of Statistics, Rice University\\
$^2$Department of Statistics, Iowa State University\\
$^3$Department of Statistics, Oregon State University}
\date{}
